Depression and suicidality as costly signals of need

### 2021-05-03 Paper.rmd
Added sources for india hh income

us_median_hh <- 68703 # census.gov
india_median_hh <- 2266 # ??

>>>>

us_median_hh <- 68703 # census.gov

# IHDS2
# Household Income Inequality and Income Mobility: Implications Towards Equalizing Longer-Term Incomes in India. By: Mishra, Aswini Kumar, International Economic Journal, 10168737, Jun2018, Vol. 32, Issue 2
#
# Table 1: per capita household income
# 	Mean	Median	Gini coefficient
# 2011–2012			
# Urban	36,101.4	22,595.0	49.0
# Rural	18,158.0	11,085.3	51.5
# Total	23,831.4	13,860.0	53.1

# 6.4 persons per household

# 13860 * 6.4 = 88704

# According to some website, in 2021 this would be
# 154,115.8 rupees (73.74% inflation), which is $2,087
india_median_hh <- 2087
